Sardines only end-to-end atlantisom test

### 2019-06-04 SardinesOnlyatlantisom2SStest.Rmd
fixing fish timing

plotB <-ggplot() +
  geom_line(data=trueB_ss, aes(x=time/stepperyr,y=atoutput, color="survey census N"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

Get true catch (may not be different from input for our project)

@@

plotcatch <- ggplot() +
  geom_line(data=truecatchbio_ss, aes(x=time,y=atoutput, color="true catch bio"),
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

Get true catch at age and other comps (may not be different from input for our project)

@@

#Atlantis initialization period
burnin <- 30

@@

######    CHECK fish_years   ####### get in right units  #######
# fishery output timestep
fstepperyr <- if(runpar$outputstepunit=="days") 365/runpar$toutfinc

#Years to fish, assuming fishing output is annual
fish_years <- burnin:(burnin+nyears-1)

#Years to survey
survey_years <- survey_sample_full[burnin:(burnin+nyears-1)]

@@

#Sample survey biomass
survObsBiom <- sample_survey_biomass(dat=survey_out,cv=cv,wtAtAge)

@@

# catch at age by area
catch_numbers <-  create_fishery_subset(dat = truth$catch,
                                         #time = fish_years,
                                         time = survey_sample_full,
                                         species = species,
                                         boxes = boxall)

# catch in numbers
catch_total <- catch_numbers %>%
  group_by(time) %>%
  summarise(catch=sum(atoutput))

@@

#Get weights
# aggregate true resn per survey or fishery subset design
catch_aggresnss <- aggregateDensityData(dat = truth$resn,
                                 #time = fish_years,
                                 time = survey_sample_full,
                                 species = species,
                                 boxes = boxall)

# aggregate true structn per survey or fishery subsetdesign
catch_aggstructnss <- aggregateDensityData(dat = truth$structn,
                                 #time = fish_years,
                                 time = survey_sample_full,
                                 species = species,
                                 boxes = boxall)

>>>>

plotB <-ggplot() +
  geom_line(data=trueB_ss, aes(x=time/stepperyr,y=atoutput, color="survey census B"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

Get true catch in tons (may not be different from input for our project)

@@

# note: time output of this file is in days
# what model timestep is this output matching?
plotcatch <- ggplot() +
  geom_line(data=truecatchbio_ss, aes(x=time/365,y=atoutput, color="true catch bio"),
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

Get true catch at age and other comps (may not be different from input for our project). First see if catch output is at same timescale as population by checking toutfinc: `r fstepperyr`

@@

#Atlantis initialization period in years
burnin <- 30

@@

#Years to fish, assuming fishing output is annual
#fish_years <- burnin:(burnin+nyears-1)
# fishery output timestep (fstepperyr in census_spec.R) for this run is 5 per year

# here we are summing the catch in numbers for input in to SS.
# To use the total catch biomass output from catch.txt the above would work 
# because the output is annual but in units of DAYS so needs time/365

#Vector of indices of catch in numbers to pull
fish_sample_full <- c(0:total_sample)
fish_burnin <- burnin*fstepperyr
fish_nyears <- nyears*fstepperyr
fish_times <- fish_sample_full[fish_burnin:(fish_burnin+fish_nyears-1)]
fish_years <- seq(fish_times[1], max(fish_times), by=fstepperyr) #last timestep

# potential problem: fish_years dont match survey_years timesteps below

#Years to survey, assuming survey is once per year
survey_years <- survey_sample_full[burnin:(burnin+nyears-1)]

@@

#Sample survey biomass
survObsBiom <- sample_survey_biomass(dat=survey_out,cv=cv,wtAtAge)
# check against survey with truth$biomass_ages output

@@

# catch at age by area
catch_numbers <-  create_fishery_subset(dat = truth$catch,
                                         time = fish_times,
                                         species = species,
                                         boxes = boxall)

if (fstepperyr>1){
  #need to take all output time steps and sum catch over each year
  #catch_numbers <- for yr in 0:nyears
  #sum catch_numbers$atoutput for time 0:fstepperyr
  #call that atoutput at time=yr+fstepperyr
  #should match fish_years
  #return the new dataset with same shape but time in endyr increments and sum nums
}

# catch in numbers summed over polygon after time has been aggregated into 1 yr
catch_total <- catch_numbers %>%
  group_by(time) %>%
  summarise(catch=sum(atoutput))

@@

#Get weights
# aggregate true resn per survey or fishery subset design
catch_aggresnss <- aggregateDensityData(dat = truth$resn,
                                 time = fish_times,
                                 species = species,
                                 boxes = boxall)

# aggregate true structn per survey or fishery subsetdesign
catch_aggstructnss <- aggregateDensityData(dat = truth$structn,
                                 time = fish_times,
                                 species = species,
                                 boxes = boxall)
